Silver Ion Chroma

### 2020-12-16 silver_ion_chroma.Rmd
fixed typo

# Summary
For those compounds observed in F1, the silver ion column resulted in an order-of-magnitude decrease in TIC. F1 was greatly depleted in hydroxy-bearing FAMES.

@@

# Protocol
A BAMES standard was run through two silver ion (Ag) columns to test the efficacy/cleanliness of the columns. A **Supelco Ag-Ion Discovery** column "Disc" and a homemade **Silver Nitrate** "Nitr" column were both tested (protocol courtesy of Nicolo Ardenghi).

@@

### Discovery Ag-Ion Column Chromatography
0. Set up Ag-Ion columns over waste colleciton vials.
1. Condition SPE with 4mL acetone
2. Equilibrate cartridge with 4mL hexane. 
3. Load FAMEs in hexane derived from sample extraction at a flow rate of 2-3 drops/second. Remove waste collection vials and replace with fraction 1 (F1) collection vials (40mL glass vials).
4. Elute F1 with 6mL hexane:acetone 96:4
*Fraction 1 targets saturated FAs, trans monoenes, cis/cis and trans/trans conjugated linoleic acids*
5. Elute F2 with 4mL hexane:acetone 90:10
*Fraction 2 will target: cis monoenes, trans/trans dienes, CLAs*
6. Elute F3 with 4mL acetone
*Fraction 3 targets cis/cis dienes, other dienes, trienes.*
7. Evaporate all fractions at 40˚C under N2, sparge.
8. Reconstituted in three 100µL hexane washes, added to a GC vial with insert.
8. Evaporated at 40˚C under N2, reconstituted in 50µL cyclohexane for GC analysis.

@@

```
Autosampler Position: Sample
37: Cyclohex Blank
38: TC-BAMES-2
39: BAMES F1 Disc
40: BAMES F2 Disc
41: BAMES F3 Disc
42: BAMES F1 Nitr
43: BAMES F2 Nitr
37: Cyclohex Blank
```

@@

## Data Import
```{r}
# Define the root directory and the path names for each file
root <- "data"
path_names = c("2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7517_TCBAMES_2_5ug_ul.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7518_BAMES_F1_Disc.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7519_BAMES_F2_Disc.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7520_BAMES_F3_Disc.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7521_BAMES_F1_Nitr.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7522_BAMES_F2_Nitr.xls")
# Define the sample names
sample_names = c("tc_bames2", "bames_disc_f1", "bames_disc_f2", "bames_disc_f3", "bames_nitr_f1", "bames_nitr_f2")

@@

## Data Cleanup
``` {r}
results <- all_data %>% 
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  # major compound groups
  mutate(
    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
  ) 
```

#Plots
Plots generated using `ggplot2` and `plotly`.

## Overview Plot
```{r, echo = FALSE, warning=FALSE}
factored_samples <- c('tc_bames2','bames_disc_f1','bames_disc_f2','bames_disc_f3', 'bames_nitr_f1', 'bames_nitr_f2', 'bames_nitr_f3')
results$sample_f = factor(results$sample, levels=factored_samples)

@@

p_tc_bames2 %>% ggplotly(dynamicTicks = TRUE)
```
```{r, echo = FALSE, warning=FALSE}
p_bames_disc_f1 <- results %>%
  filter(sample == c("bames_disc_f1")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  scale_fill_viridis_d() +
  labs(title = "BAMES Discovery Ag-Ion F1", subtitle = "saturated FAs, trans monoenes, cis/cis and trans/trans conjugated linoleic acids") +
  theme_bw()

p_bames_disc_f1 %>% ggplotly(dynamicTicks = TRUE)
```
```{r, echo = FALSE, warning=FALSE}
p_bames_disc_f2 <- results %>%
  filter(sample == c("bames_disc_f2")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  scale_fill_viridis_d() +
  labs(title = "BAMES Discovery Ag-Ion F2", subtitle = "cis monoenes, trans/trans dienes, CLAs") +
  theme_bw()

@@

p_bames_disc_f3 %>% ggplotly(dynamicTicks = TRUE)
```
```{r, echo = FALSE, warning=FALSE}
p_bames_nitr_f1 <- results %>%
  filter(sample == c("bames_nitr_f1")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  scale_fill_viridis_d() +
  labs(title = "BAMES Ag - Nitrate F1") +
  theme_bw()

>>>>

# Summary

For those compounds observed in F1, the silver ion column resulted in an order-of-magnitude decrease in TIC. F1 was greatly depleted in hydroxy-bearing FAMES.

@@

# Protocol

A BAMES standard was run through two silver ion (Ag) columns to test the efficacy/cleanliness of the columns. A **Supelco Ag-Ion Discovery** column "Disc" and a homemade **Silver Nitrate** "Nitr" column were both tested (protocol courtesy of Nicolo Ardenghi).

@@

### Discovery Ag-Ion Column Chromatography

0.  Set up Ag-Ion columns over waste collection vials.
1.  Condition SPE with 4mL acetone
2.  Equilibrate cartridge with 4mL hexane.
3.  Load FAMEs in hexane derived from sample extraction at a flow rate of 2-3 drops/second. Remove waste collection vials and replace with fraction 1 (F1) collection vials (40mL glass vials).
4.  Elute F1 with 6mL hexane:acetone 96:4 *Fraction 1 targets saturated FAs, trans monoenes, cis/cis and trans/trans conjugated linoleic acids*
5.  Elute F2 with 4mL hexane:acetone 90:10 *Fraction 2 will target: cis monoenes, trans/trans dienes, CLAs*
6.  Elute F3 with 4mL acetone *Fraction 3 targets cis/cis dienes, other dienes, trienes.*
7.  Evaporate all fractions at 40˚C under N2, sparge.
8.  Reconstituted in three 100µL hexane washes, added to a GC vial with insert.
9.  Evaporated at 40˚C under N2, reconstituted in 50µL cyclohexane for GC analysis.

@@

```{=html}
<!-- -->
```
    Autosampler Position: Sample
    37: Cyclohex Blank
    38: TC-BAMES-2
    39: BAMES F1 Disc
    40: BAMES F2 Disc
    41: BAMES F3 Disc
    42: BAMES F1 Nitr
    43: BAMES F2 Nitr
    37: Cyclohex Blank

@@

## Data Import

```{r}
# Define the root directory and the path names for each file
root <- "data"
path_names = c("2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7517_TCBAMES_2_5ug_ul.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7518_BAMES_F1_Disc.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7519_BAMES_F2_Disc.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7520_BAMES_F3_Disc.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7521_BAMES_F1_Nitr.xls",
          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7522_BAMES_F2_Nitr.xls")
# Define the sample names
sample_names = c("tc_bames2", "bames_disc_f1", "bames_disc_f2", "bames_disc_f3", "bames_nitr_f1", "bames_nitr_f2")

@@

## Data Cleanup

```{r}
results <- all_data %>% 
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  # major compound groups
  mutate(
    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
  ) 
```

\#Plots Plots generated using `ggplot2` and `plotly`.

## Overview Plot

```{r, echo = FALSE, warning=FALSE}
factored_samples <- c('tc_bames2','bames_disc_f1','bames_disc_f2','bames_disc_f3', 'bames_nitr_f1', 'bames_nitr_f2', 'bames_nitr_f3')
results$sample_f = factor(results$sample, levels=factored_samples)

@@

p_tc_bames2 %>% ggplotly(dynamicTicks = TRUE)
```

```{r, echo = FALSE, warning=FALSE}
p_bames_disc_f1 <- results %>%
  filter(sample == c("bames_disc_f1")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  scale_fill_viridis_d() +
  labs(title = "BAMES Discovery Ag-Ion F1", subtitle = "saturated FAs, trans monoenes, cis/cis and trans/trans conjugated linoleic acids") +
  theme_bw()

p_bames_disc_f1 %>% ggplotly(dynamicTicks = TRUE)
```

```{r, echo = FALSE, warning=FALSE}
p_bames_disc_f2 <- results %>%
  filter(sample == c("bames_disc_f2")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  scale_fill_viridis_d() +
  labs(title = "BAMES Discovery Ag-Ion F2", subtitle = "cis monoenes, trans/trans dienes, CLAs") +
  theme_bw()

@@

p_bames_disc_f3 %>% ggplotly(dynamicTicks = TRUE)
```

```{r, echo = FALSE, warning=FALSE}
p_bames_nitr_f1 <- results %>%
  filter(sample == c("bames_nitr_f1")) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  scale_fill_viridis_d() +
  labs(title = "BAMES Ag - Nitrate F1") +
  theme_bw()
